\paperTitle

### 2014-01-31 doc/icml2014/directed.tex
Fixed TODO with asymptotic estimators stuff
Fixed reduction2

Note that in each of the above cases,
each hidden variable $h_i$ of the clique has its own view which is conditionally independent
given the other variables in the clique.
%Fundamentally, algorithm takes advantage of having a view for every
  %hidden variable in a clique to help identify its hidden state.
We capture this general property as follows:
\begin{property}(Exclusive views)
  \label{prop:exclusive-views}
  A clique $\sC$ of $\sG$ is said to possess \textbf{exclusive views property} if for every hidden variable $h_i \in \sC$,
  there is some observed variable, $x_{v}$, which is conditionally
  independent of the rest of the clique given $h_i$.
  and whose conditional
  moment $\mOpp{v}{i} \eqdef \Pr(x_{v} \mid h_i)$ can be estimated consistently.
We call $x_v$ the exclusive view of $h_i$ in $\sC$.
\end{property}

@@

We can now use the delta-method to convert the above result into 
the asymptotic variance for the pseudoinverse version of $\LearnClique$:
\begin{lemma}[Asymptotic variance of pseudoinverse estimator for $Z_\sC$]
  \label{lem:mom-variance}  
  Assume $\hat M_{\sV}$ has asymptotic variance $\Sigma_\sV$ defined above.
  Then the asymptotic variance of $Z_\sC$ is:
  \begin{align*}
    \Sigma^{\mom} &= \mOppAlli \Sigma_\sV \mOppAllit,
  \end{align*}
  where $\pinv{\mOppAll} \eqdef \pinv{\mOpp{v_1}{i_1}} \otimes
  \cdots \otimes \pinv{\mOpp{v_m}{i_m}}$, a $d^m \times k^m$ matrix.
\end{lemma}
\begin{proof}
For clique $\sC$, recall we have
  $Z_{\sC} = \mO_\sV(\mOppi{v_1}{i_1},\cdots,\mOppi{v_m}{i_m})$.
%Choosing to represent $Z_\sC$ and $M_\sV$ as vectors and
%$\mOppi{v_1}{i_1} \otimes \cdots \otimes \mOppi{v_m}{i_m}$ as the
%matrix,
We can rewrite this representation more compactly as: $Z_{\sC} = \pinv{\mOppAll} \mO_\sV$.
By the delta-method \cite{vaart98asymptotic},
% DONE: need to shorten
%we have that the asymptotic variance of $M_\sV$ is:
%\begin{align*}
%  \sqrt{n}(\hat M_\sV - M_\sV) \convind \sN(0, \Sigma_\sV),
%\end{align*}
%where $\Sigma_\sV$ is the variance of the observations. 
we immediately get:
$\sqrt{n}(\hat Z_\sC - Z_\sC) \convind \sN(0, \mOppAlli \Sigma_\sV \mOppAllit)$.
\end{proof}

>>>>

Note that in each of the above cases,
  for any clique $\sC$, each hidden variable $h_i \in \sC$ has its own
  view which is conditionally independent
given the other variables in the clique.
%Fundamentally, algorithm takes advantage of having a view for every
  %hidden variable in a clique to help identify its hidden state.
We capture this general property as follows:
\begin{property}(Exclusive views)
  \label{prop:exclusive-views}
  A clique $\sC$ of $\sG$ is said to possess \textbf{exclusive views property} if for every hidden variable $h_i \in \sC$,
  there is some observed variable, $x_{v}$, which is conditionally
  independent of the rest of the clique given $h_i$.
  and whose conditional
  moment $\mOpp{v}{i} \eqdef \Pr(x_{v} \mid h_i)$ can be estimated consistently.
We call $x_v$ the exclusive view of $h_i$ in $\sC$.
\end{property}

@@

We can now use the delta-method to convert the above result into 
the asymptotic variance for the pseudoinverse version of $\LearnClique$:
\begin{lemma}[Asymptotic variance of pseudoinverse estimator for $Z_\sC$]
  \label{lem:mom-variance}  
  Assume $\hat M_{\sV}$ has asymptotic variance $\Sigma_\sV$ defined above.
  Then the asymptotic variance of $\hat Z_\sC$ is:
  \begin{align*}
    \Sigma^{\mom} &= \mOppAlli \Sigma_\sV \mOppAllit,
  \end{align*}
  where $\pinv{\mOppAll} \eqdef \pinv{\mOpp{v_1}{i_1}} \otimes
  \cdots \otimes \pinv{\mOpp{v_m}{i_m}}$, a $d^m \times k^m$ matrix.
\end{lemma}
\begin{proof}
For clique $\sC$, recall we have
  $Z_{\sC} = \mO_\sV(\mOppi{v_1}{i_1},\cdots,\mOppi{v_m}{i_m})$.
%Choosing to represent $Z_\sC$ and $M_\sV$ as vectors and
%$\mOppi{v_1}{i_1} \otimes \cdots \otimes \mOppi{v_m}{i_m}$ as the
%matrix,
We can rewrite this representation more compactly as: $Z_{\sC} = \pinv{\mOppAll} \mO_\sV$.
By the delta-method \cite{vaart98asymptotic},
% DONE: need to shorten
%we have that the asymptotic variance of $M_\sV$ is:
%\begin{align*}
%  \sqrt{n}(\hat M_\sV - M_\sV) \convind \sN(0, \Sigma_\sV),
%\end{align*}
%where $\Sigma_\sV$ is the variance of the observations. 
we immediately get:
$\sqrt{n}(\hat Z_\sC - Z_\sC) \convind \sN(0, \mOppAlli \Sigma_\sV \mOppAllit)$.
\end{proof}
